Uncertainty in the evolution of social learning

### 2022-05-12 ms.tex
merged overleaf

>>>>

\subsection{The history of "copy when uncertain"}
It has become a near truism that "theory predicts that it is adaptive to learn when uncertain."
This claim has been motivated by empirical work (such as Asch conformism studies) \& theoretical models (Boyd Richerson 85, 88) that often do not mention the word uncertainty at all. However, they do show related effects of social learning increasing when individual learning is difficult (i.e., ambiguous lines in Asch), and intermediate levels of temporal uncertainty favoring social learning (i.e., too stable and you get genetic canalization of a trait, too much temporal variation and there's selection for individual learning to ensure the most up to date information).

{Galef 2009} https://www.sciencedirect.com/science/article/pii/S006534540939004X\#bb0059
cites {B \& R 85/88 \& Laland 2004} https://link.springer.com/content/pdf/10.3758/BF03196002.pdf
Laland 2004 cites {B\& R 88}
\url{https://books.google.com/books?hl=en&lr=&id=mqFcAgAAQBAJ&oi=fnd&pg=PA29&dq=Boyd+and+Richerson\%E2\%80\%99s+(1988&ots=IfIbB_kx_a&sig=g8CYH5bVfwfXhTRGot0q761f9mw\#v=onepage&q&f=false}

Other examples of empirical work: https://www.sciencedirect.com/science/article/pii/S0022096516300625

Henrich \& Boyd 88 do have something like B that is the difficulty of getting right answer (or rho probability of doing so)
https://www.sciencedirect.com/science/article/pii/S109051389800018X\#FIG5

Lifespan not modelled

\subsection{earlier structure}
